Bootstrap with a grid

### 2024-07-23 Boot_grid.Rmd
Correct bootstrap with grid

```{r}
# Sample size
n <- 1000
```

@@

MonteCarlo <- function(n, B, f){
  # n: sample size; 
  # B: number of iterations for MC; 
  # f: function to consider (with 2 variables, x and y)

  p <- sum(rep((1/1000)*(1/1000), n)) # inclusion density
  est_MC <- c() # Vector containing all estimations
  for (b in 2:B) { # All in one "for" loop
    # Uniform sampling over the whole territory
    a1 <- runif(n, 0, 1000)
    a2 <- runif(n, 0, 1000)
    # Variable of interest derived from the sample
    a <- mapply(f, a1, a2)
    est_MC <- append(est_MC, sum(a/p))
  }

@@

MC_boot <- function(n, B1, B2, f){
  # n: sample size; B1: number of iterations for MC;
  # B2: number of iterations for bootstrap;
  # f: function to consider (2 arguments)

  p <- sum(rep((1/1000)*(1/1000), n))
  var_est_boot <- c()
  for (b in 2:B1) {
    # One MC iteration at a time
    random_points <- data.frame(x = runif(n, 0, 1000), y = runif(n, 0, 1000))
    random_points$var <- mapply(f, random_points[, 1], random_points[, 2])
    a <- sum(random_points$var/p)

@@

res1_nb <- MonteCarlo(n, 10000, circle_nb)
# Just one circle to begin with

@@

res2_nb <- MC_boot(n, B1 = 1000, B2 = 400, f = circle_nb)
# Just one circle to begin with

@@

```{r}
cat("Mean of the variance of bootstrap samples:", res2_nb)
# Examples:
# Mean of the variance of bootstrap samples: 2845120
# Mean of the variance of bootstrap samples: 2851631
```

```{r}
cat("We get a difference of: ", 100*(max(res1_nb,res2_nb)-min(res1_nb,res2_nb))/min(res1_nb,res2_nb), "%", sep = "")
# Examples:
# We get a difference of: 2.01084%
# We get a difference of: 0.8599411%
```

@@

res1_vol <- MonteCarlo(n, 10000, circle_vol)
# Just one circle to begin with

@@

res2_vol <- MC_boot(n, B1 = 1000, B2 = 400, f = circle_vol)
# Just one circle to begin with

>>>>

```{r}
i <- sample(1:10, 1) # choice of the rank of the identifier we want
i
```

```{r}
# Dimension of a small square (length of one side of the square)
# We assume that c_dim is a divisor of 1000
c_dim <- 10
```

```{r}
# Function to sample at random following the grid
sampling_grid <- function(i,c_dim){
random_points <- data.frame(x = numeric(), y = numeric())

for (l in 0:((1000/c_dim)-1)) {
  if (l==0){
    x_init <- i*c_dim
  }else if ((3*l+i)*c_dim < (10)*c_dim){
    x_init <- (3*l+i)*c_dim
  }else{
    x_init <- (((3*l+i)*c_dim)%%(c_dim*10))
  }
  k <- 0
  while (x_init + 10*c_dim*k < 1000) {
    a <- runif(1, x_init + 10*c_dim*k, x_init + 10*c_dim*k + c_dim)
    b <- runif(1, l*c_dim, (l+1)*c_dim)
    random_points <- rbind(random_points, list(a,b))
    k <- k+1
  }
}
colnames(random_points) <- list("x", "y")
return(random_points)
}
```

@@

MonteCarlo <- function(B, f){
  # B: number of iterations for MC; 
  # f: function to consider (with 2 variables, x and y)

  est_MC <- c() # Vector containing all estimations
  for (b in 2:B) { # All in one "for" loop
    # Sampling over the whole territory
    df_grid <- sampling_grid(i,c_dim)
    # Variable of interest derived from the sample
    a <- mapply(f, df_grid$x, df_grid$y)
    n <- nrow(df_grid)
    p <- sum(rep((1/1000)*(1/1000), n)) # inclusion density
    est_MC <- append(est_MC, sum(a/p))
  }

@@

MC_boot <- function(B1, B2, f){
  # B1: number of iterations for MC;
  # B2: number of iterations for bootstrap;
  # f: function to consider (2 arguments)

  var_est_boot <- c()
  for (b in 2:B1) {
    # One MC iteration at a time
    random_points <- sampling_grid(i,c_dim)
    random_points$var <- mapply(f, random_points[, 1], random_points[, 2])
    n <- nrow(random_points)
    p <- sum(rep((1/1000)*(1/1000), n))
    a <- sum(random_points$var/p)

@@

res1_nb <- MonteCarlo(10000, circle_nb)
# Just one circle to begin with

@@

res2_nb <- MC_boot(B1 = 1000, B2 = 400, f = circle_nb)
# Just one circle to begin with

@@

```{r}
cat("Mean of the variance of bootstrap samples:", res2_nb)
# Example:
# Mean of the variance of bootstrap samples: 
```

```{r}
cat("We get a difference of: ", 100*(max(res1_nb,res2_nb)-min(res1_nb,res2_nb))/min(res1_nb,res2_nb), "%", sep = "")
# Example:
# We get a difference of: 
```

@@

res1_vol <- MonteCarlo(10000, circle_vol)
# Just one circle to begin with

@@

res2_vol <- MC_boot(B1 = 1000, B2 = 400, f = circle_vol)
# Just one circle to begin with
